FraCaS: Temporal Analysis

### 2020-11-09 paper2020/paper.tex
clarify FraCaS extension status

Another thing that we are willing to try is an extension of the FraCaS
test suite that will include more fine-grained examples of lexical and
grammatical aspect, as well as the interaction between those two, for example
cases where one needs to actually distinguish between achievements and
accomplishments on the basis of their inferential properties:

@@

%Another issue to be looking at is the codification of lexical
%aspect.\todo{update} In what we have been doing so far, we did not distinguish
%between the present continuous and the present or the simple past and
%the past continuous and their interaction with non-lexical aspect.
%The main reason for this is that in the test suite, even though there
%are examples of inferences based on the either lexical or non-lexical
%aspect, no example where an interaction between the two exists. For
%example, one such case is the one shown below and exemplifies the
%difference between activities and accomplishments with respect to the
%different inferences they give when used in the past continuous:

>>>>

Another extension of this work is to reflect more temporal semantic
inference properties in an extended test suite. Indeed, there as properties which are
not captured in the FraCaS test suite, such as fine-grained examples of lexical and
grammatical aspect, as well as the interaction between those two, for example
cases where one needs to actually distinguish between achievements and
accomplishments on the basis of their inferential properties:

@@
